---
title: "fracture_segmentation_plots"
author: "Scott McKean"
date: "1/31/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
source('ecdf.R')
```

Scanlines

```{r}
scanline_df = read_csv('G:/My Drive/PhD/Analysis/EvanThomas_Montney/horizontal_scanlines_South_Wall_50cm.csv')

ggplot(scanline_df) +
  geom_line(aes(x = y_coord, y = p10_trimmed)) +
  geom_point(aes(x = y_coord, y = p10_trimmed)) +
  geom_area(aes(x = y_coord, y = p10_trimmed)) +
  coord_flip() +
  theme_minimal() +
  ggsave('horiz_scanline.eps', height = 10, width = 2)

```

Windows

```{r}
windows = read_csv('G:/My Drive/PhD/Analysis/EvanThomas_Montney/windows_SouthWall_10m+5m.csv')
scale = 0.002069

# Filter windows here if (masked_area)/(orig_area) > x remove
windows_filt = windows %>% 
  dplyr::filter(masked_area/orig_area > 0.75)

#P20
ggplot(windows_filt  %>% dplyr::filter(!is.na(p20_masked) & p20_masked > 0)) +
  geom_tile(aes(x=x_coord/scale, y=y_coord/scale, fill = p20_masked)) +
  scale_fill_gradientn(colors = viridis_pal(option = 'inferno')(10), #limits=c(0, 5),
                       na.value = "#FCFFA4FF") +
  theme_minimal() +
  coord_equal() + 
  ggsave('window_p20_heatmap.eps')

#P21
ggplot(windows_filt %>% dplyr::filter(!is.na(p21_masked) & p21_masked > 0)) +
  geom_tile(aes(x=x_coord/scale, y=y_coord/scale, fill = p21_masked)) +
  scale_fill_gradientn(colors = viridis_pal(option = 'magma')(10), #limits=c(0, 5),
                       na.value = "#FCFDBFFF") +
  theme_minimal() +
  coord_equal() +
  ggsave('window_p21_heatmap.eps')
```

Spacing Dataframe - Binned ECDF Plot

```{r}
spacing_df = read_csv('G:/My Drive/PhD/Analysis/EvanThomas_Montney/horiz_scanline_spacing_SouthWall_50cm.csv')

# method = 'freedman', 'rice', or 'sturges'
for (this_name in unique(spacing_df$name)[1:200]){
  this_spacing_df = spacing_df %>% dplyr::filter(name == this_name)
  
  # skip all ECDFs with less than n observations
  if(nrow(this_spacing_df) <= 5) next
  
  ecdf = make_ecdf(this_spacing_df$height, method = 'rice') %>%
    dplyr::mutate(ecdf_norm = ecdf/nrow(.))

  ggplot(ecdf) +
    geom_point(aes(x = centres, y = ecdf)) +
    geom_line(aes(x = centres, y = ecdf)) +
    scale_x_log10() +
    xlim(.0001,1) +
    scale_y_log10() +
    theme_minimal() +
    ggtitle(this_name) +
    ylab('Log N') +
    xlab('Log Fracture Height (m)') +
    ggsave(paste0(this_name,'binned_height_ecdf.eps'), height = 6, width = 6) +
    ggsave(paste0(this_name,'binned_height_ecdf.eps'), height = 6, width = 6, dpi = 320)
}

```

Danny's Implementation <3

```{r}
for (this_name in unique(spacing_df$name)[1:300]){
  
  # skip all ECDFs with less than n observations
  if(nrow(this_spacing_df) <= 5) next
  
  scanline_length = scanline_df %>% 
    filter(name==this_name) %>%
    pull(trimmed_length)
  
  heights = spacing_df %>% 
    dplyr::filter(name == this_name) %>%
    pull(height)
  
  output = rev_ecdf(heights) %>%
    dplyr::mutate(height = value,
                  intensity = count/scanline_length)
  
  #Make Plot
  ggplot(output) +
    geom_point(aes(x = height, y = intensity)) +
    geom_line(aes(x = height, y = intensity)) +
    scale_x_log10(limits=c(0.01,2))+
    scale_y_log10(limits=c(0.0001,1))+
    theme_minimal() +
    ggtitle(this_name) +
    ggsave(paste0(this_name,'height_ecdf.eps'), height = 6, width = 6) +
    ggsave(paste0(this_name,'height_ecdf.jpg'), height = 6, width = 6, dpi = 320)
}
```

